A Case Study in Preserving a High Energy Physics Application

### 2014-02-26 paper.tex
modify script pic of version4;

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        {\bf Version 1: Email}\\ \hline
        1. Create a CMS release,\\
            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3\_11\_patch3 \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} https://github.com/cms-ttH/BEAN/blob/...\\
        3. Install grid-control: \\ 
            \hspace{9pt} svn co https://ekptrac.physik.uni-ka/... \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} git clone https://github.com/matz-e/... \\
           \hspace{9pt} scram b -j32 \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \hline
        {\bf Version 2: Script}\\ \hline
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone https://github.com/cms-ttH/BEAN.git \\
        wget -r http://nd.edu/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget http://pyyaml.org/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv\\
        python setup.py install --user \\
        scripts/roaster data/generic\_ttl.yaml \\ 
        \hline
        {\bf version 3: Formulated Script} \\ \hline
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        set {\bf GIT} = (https://github.com) \\
        set {\bf PYYAML} = (http://pyyaml.org) \\
        set {\bf ND} = (http://nd.edu) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv\\
        python setup.py install --user \\
        scripts/roaster data/generic\_ttl.yaml \\ 
        \hline
        {\bf Version 4: Fine-Grained Toolkit}\\ \hline
        \#deploy software environment using /archive \\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        set {\bf GIT} = /archive/git \\
        set {\bf CMSSW} = /archive/CMSSW \\
        set {\bf HTTP} = /archive/http \\
        set {\bf EXP} = /archive/experiment\\
        set {\bf GRID} = /archive/grid-data \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        archive\_get \${\bf CMSSW}/...\\
        archive\_get \${\bf GIT}/cms-ttH/BEAN.git \\
        archive\_get \${\bf EXP}/nd.edu/~abrinke1/... \\        
        archive\_get \${\bf HTTP}/PyYAML/...\\
        archive\_get \${\bf GRID}/...\\
        scram b -j32 \\
        cmsenv\\
        python setup.py install --user \\
        scripts/roaster data/generic\_ttl.yaml \\
        \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

@@

One new version of the analysis script will be generated for the reproduction
of the original experiment. The Version 4 of Table~\ref{table:scripts} illustrates the format of
this new version. The environment variables of dependencies refer to the
storage path inside the archive.  One utility, archive\_get,  is created to
help the new user to obtain data from the remote archive.
Table~\ref{table:archive-map} illustrates the structure of the remote archive.
/archive/OS includes the images of different Operating Systems.
/archive/software integrates all the commonly used software, such as git,
python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
Grid. /archive/experiment includes the all the experiments submitted into the
archive. The private files and description files of each experiment will be
organized together.

>>>>

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        {\bf Version 1: Email}\\ \hline
        1. Create a CMS release,\\
            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} {\tt https://github.com/cms-ttH/BEAN/blob/...}\\
        3. Install grid-control: \\ 
            \hspace{9pt} {\tt svn co https://ekptrac.physik.uni-ka/...} \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} {\tt git clone https://github.com/matz-e/...} \\
           \hspace{9pt} {\tt scram b -j32} \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \hline
        {\bf Version 2: Script}\\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone {\tt https://github.com/cms-ttH/BEAN.git}} \\
        {\tt wget -r http://nd.edu/~abrinke1/ElectronEffectiveArea.h} \\
        {\tt scram b -j32} \\
        {\tt wget http://pyyaml.org/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
        {\bf version 3: Formulated Script} \\ \hline
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        set {\bf GIT} = (https://github.com) \\
        set {\bf PYYAML} = (http://pyyaml.org) \\
        set {\bf ND} = (http://nd.edu) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv\\
        python setup.py install --user \\
        scripts/roaster data/generic\_ttl.yaml \\ 
        \hline
        {\bf Version 4: Fine-Grained Toolkit}\\ \hline
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        set {\bf GIT} = (https://github.com) \\
        set {\bf PYYAML} = (http://pyyaml.org) \\
        set {\bf ND} = (http://nd.edu) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\ 
        cmsenv\\
        python setup.py install --user \\
        scripts/roaster data/generic\_ttl.yaml \\
        \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

@@

Table~\ref{table:archive-map} illustrates the structure of the remote archive.
\path{/archive/OS} includes the images of different Operating Systems.
/archive/software integrates all the commonly used software, such as git,
python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
Grid. \path{/archive/experiment} includes the all the experiments submitted into the
archive. The private files and description files of each experiment will be
organized together.

The Version 4 of Table~\ref{table:scripts} illustrates the script used in
Solution 4, which is the same as the one used in Solution 3. 
However, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file redirects the git access path into /archive/git from the original path (http://github.com) referred in the script.
This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the archive only introduces the minimal changes of the map file.
